---
title: "Assignment 2 - Differential Gene Expression and Preliminary ORA"
author: "Anna Teresa Lai"
email: annateresa.lai@mail.utoronto.ca
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
geometry: left = 2cm, right = 2cm, top = 1cm, bottom = 1cm
mainfont: Courier
bibliography: assignment2.bib
csl: bioinformatics.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
suppressPackageStartupMessages({
  library('GEOquery')
  library('BiocManager')
  library("edgeR")
  library("biomaRt")
  library("GEOmetadb")
  library("R.utils")
  library("ggplot2")
  library("rpact")
  })
```

# Introduction 
The data was cleaned and pre-processed in the previous assignment. The data was published on a [2020 paper](10.1038/s41467-020-16589-8 )[@perkail2020bap1]. Citation of Bioinformatics journal style was used. The styling of this citation was downloaded from GitHub. 

# Expression

# Over-representation analysis

# References

## Citation of packages and GitHub resources used
```{r}
# csl file citation: https://github.com/citation-style-language/styles/blob/master/bioinformatics.csl
```

## Citations generated with bibtex
